\cvsection{Work Experience}

\begin{cventries}

	\cventry
	{Sr. Software Engineer and Team Lead}
	{Chartbeat}
	{New York, New York}
	{June 2015 - Present}
	{
		\begin{cvitems}
		\item {Architected and built a realtime streaming backend using Apache Kafka, Clojure, Riak, and AWS DynamoDB for "New Heads Up Display", a product that translates 300K req/sec into 100mil click events per minute exposed via a site-overlay-dashboard to the user in < 15 sec.}
		\item {Adopted Scrum-like process to organize and lead a 9-person team to successful product launch after a year of set-backs. Applied same process to later teams to fix existing products and build new reporting infrastucture.}
		\item {Primary Maintainer of Clojure-Kafka internal libraries, Kafka consumer best practices, and highest load Kafka consumers.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{Software Engineer}
	{}
	{}
	{June 2013 - June 2015}
	{
		\begin{cvitems}
		\item {Primary backend engineer in rebuilding Chartbeat Video Product which shows customers information about their video content.}
		\item {Architected and built historical and realtime ETL-pipelines targetting MongoDB and AWS Redshift.}
		\item {Architected and built supporting worker and API infrastructure for generating reports and dashboards.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{Software Engineer - Contractor}
	{Involvio}
	{New York, New York}
	{December 2012 - May 2013}
	{
		\begin{cvitems}
		\item {Migrated an existing PHP application to Ruby on Rails.}
		\item {Restructured the exsisting application's use of MongoDB for 10x improved performance.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{HackNY Fellow}
	{Branch, Branch.com}
	{New York, New York}
	{December 2012 - May 2013}
	{
		\begin{cvitems}
		\item {Worked as a full-stack Ruby on Rails developer to help branch.com launch as a new product on a team of less than 10 people.}
		\item {Participated in the HackNY Fellowship program which involved collaborating with other fellows on projects and attending talks from industry leaders.}
		\end{cvitems}
	}

\end{cventries}
